\section{Strings}
  \subsectionRed{Knuth-Morris-Pratt}
    Count and find all matches of string $f$ in string $s$ in $O(n)$ time.
    \code{strings/kmp.cpp}
  \subsection{Trie}
    \code{strings/trie.cpp}
    \subsubsection{Persistent Trie}
      \code{strings/trie_persistent.cpp}
  \subsectionRed{Suffix Array}
    Construct a sorted catalog of all substrings of $s$ in $O(n \log n)$ time using counting sort.
    \code{strings/suffix-array.cpp}
  \subsectionRed{Longest Common Prefix}
    Find the length of the longest common prefix for every substring in $O(n)$.
    \code{strings/lcp.cpp}
  \subsectionRed{Aho-Corasick Trie}
    Find all multiple pattern matches in $O(n)$ time. This is KMP for multiple strings.
    \code{strings/aho-corasick-trie.java}
  \subsection{Palimdromes}
    \subsubsectionRed{Palindromic Tree}
      Find lengths and frequencies of all palindromic substrings of a string in $O(n)$ time.

      Theorem: there can only be up to $n$ unique palindromic substrings for any string.
      \code{strings/palindromic-tree.cpp}
    \subsubsection{Eertree}
      \code{strings/eertree.cpp}
  \subsection{Z Algorithm}
    Find the longest common prefix of all substrings of $s$ with itself in $O(n)$ time.
    \code{strings/z.cpp}
  \subsectionRed{Booth's Minimum String Rotation}
    Booth's Algo: Find the index of the lexicographically least string rotation in $O(n)$ time.
    \code{strings/booth.cpp}
	\subsection{Hashing}
    \subsubsection{Rolling Hash}
      \code{strings/rolling_hash.cpp}
